Flabby and injective objects in toposes

### 2023-05-01 paper-flabby-objects.tex
to do

>>>>

https://www.math.uni-duesseldorf.de/~schroeer/publications_pdf/FlasqueSheaves.pdf
and reference 17 there

Remark that our flabby hulls are not qcoh in general

Bell, J. L. (1997). Zorn’s lemma and complete Boolean algebras in
intuitionistic type theories. The Journal of Symbolic Logic, 62(04),
1265–1279.

Grothendieck's letter to Larry Breen in 1975: doing without injective
resolutions
